\documentclass[twocolumn]{aastex62}

\bibliographystyle{aasjournal}
\usepackage{subfigure}
\usepackage{url}
\usepackage{hyperref}
%\usepackage{datetime}
\usepackage{longtable}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{listings}
\usepackage[normalem]{ulem}
\usepackage{bm}
\usepackage{comment}
% additions for ease of tabling
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
% colors
%\usepackage[usenames, dvipsnames]{color}

%\usepackage{pdflscape}
\usepackage{xcolor, fontawesome}
\definecolor{twitterblue}{RGB}{64,153,255}
\newcommand{\twitter}[1]{\href{https://twitter.com/#1 }{\textcolor{twitterblue}{\faTwitter}\,\tt \textcolor{twitterblue}{@#1}}}

\definecolor{Code}{rgb}{0,0,0}
\definecolor{Decorators}{rgb}{0.5,0.5,0.5}
\definecolor{Numbers}{rgb}{0.5,0,0}
\definecolor{MatchingBrackets}{rgb}{0.25,0.5,0.5}
\definecolor{Keywords}{rgb}{1,0,0}
\definecolor{self}{rgb}{0,0,0}
\definecolor{Strings}{rgb}{0,0.63,0}
\definecolor{Comments}{rgb}{0,0.63,1}
\definecolor{Backquotes}{rgb}{0,0,0}
\definecolor{Classname}{rgb}{0,0,0}
\definecolor{FunctionName}{rgb}{0,0,0}
\definecolor{Operators}{rgb}{0,0,0}
\definecolor{Background}{rgb}{0.98,0.98,0.98}
\definecolor{Booleans}{rgb}{0.572,0,0.572}
\definecolor{BuiltinFunction}{rgb}{0.572,0,0.572}
\definecolor{BuiltinConstant}{rgb}{0.572,0,0.572}
\definecolor{Asterisk}{rgb}{0.670,0,1}

\lstdefinelanguage{Python}{
    	numbers=left,
    	numberstyle=\footnotesize,
    	numbersep=7pt,
    	xleftmargin=1.26em,
    	framextopmargin=2em,
    	framexbottommargin=2em,
    	showspaces=false,
    	showtabs=false,
    	showstringspaces=false,
    	frame=l,
    	tabsize=4,
    	stepnumber=1,
	% Basic
	basicstyle=\small\ttfamily,
    	backgroundcolor=\color{Background},
%    	breaklines=True,
%    	postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space},
	% Comments
%	commentstyle=\color{green}\ttfamily,
	% Strings
%    	stringstyle=\ttfamily\color{Strings},
%    	morecomment=[s][\color{Strings}]{'}{'}, 
%    	stringstyle=\ttfamily\color{Comments},
%    	morecomment=[s][\color{Comments}]{\#}{\#}, 			
	% Keywords
	stringstyle=\ttfamily\color{Strings},
	morekeywords={import,from,class,def,while,if,in,elif,else,not,or,print,break,continue,return,access,as,except,exec,finally,global,import,lambda,pass,print,raise,try,assert},
    	keywordstyle={\color{Keywords}\bfseries}, 
    %	morekeywords={[2]True,False,None},
    %	keywordstyle={[2]\color{BuiltinConstant}\slshape},
	otherkeywords={[2]*},
	keywordstyle={[2]\color{Asterisk}},
%	emph={self},
%	emphstyle={\color{self}\slshape}	
}

\usepackage{color}

\newcommand{\ron}{\color{red}} 
\newcommand{\bon}{\color{blue}} 
\newcommand{\gon}{\color{green}} 
\newcommand{\coff}{\color{black}\,}
\newcommand{\shrug}{\texttt{\raisebox{0.75em}{\char`\_}\char`\\\char`\_\kern-0.5ex(\kern-0.25ex\raisebox{0.25ex}{\rotatebox{45}{\raisebox{-.75ex}"\kern-1.5ex\rotatebox{-90})}}\kern-0.5ex)\kern-0.5ex\char`\_/\raisebox{0.75em}{\char`\_}}}


\newcommand{\rprs}{{$R_p/R_{\star}$}}

\newcommand{\eg}{{\it e.g.}}
\newcommand{\ie}{{\it i.e.}}
\newcommand{\kep}{{\it Kepler}}
\newcommand{\kt}{{\it K2}}
\newcommand{\tess}{{\it TESS}}
\newcommand{\ffis}{Full-Frame Images}
\newcommand{\fulltess}{{\it Transiting Exoplanet Survey Satellite}}
\newcommand{\Gaia}{{\it Gaia}}
\newcommand{\spitz}{{\it Spitzer}}
\newcommand{\vsini}{{$V \sin i$}}
\newcommand{\teff}{$T_{ eff}$}
\newcommand{\kms}{{km\,s$^{-1}$}}
\newcommand{\gcc}{{g\,cm$^{-3}$}}
\newcommand{\rstar}{{$R_\star$}}
\newcommand{\rhostar}{{$\rho_\star$}}
\newcommand{\mearth}{{M$_\oplus$}}
\newcommand{\rearth}{{R$_\oplus$}}
\newcommand{\rsun}{{R$_\odot$}}
\newcommand{\msun}{{M$_\odot$}}
\newcommand{\mjup}{{M$_\textrm{Jup}$}}
\newcommand{\rjup}{{R$_\textrm{Jup}$}}

\newcommand{\eleanor}{\texttt{eleanor}}

\newcommand{\mstar}{{$M_\star$}}
\newcommand{\logg}{{log(g)}}
\newcommand{\mh}{{[M/H]}~}
\newcommand{\feh}{{[Fe/H]}~}
%\newcommand{\h2ok2}{{$ H_2O-K2$}}

\newcommand{\todo}[3]{{\color{#2} \emph{#1} TO DO: #3}}
\newcommand{\mkntodo}[1]{\todo{ADINA}{cyan}{#1}}
\newcommand{\btmtodo}[1]{\todo{BEN}{blue}{#1}}
\newcommand{\anytodo}[1]{\todo{ANYONE}{green}{#1}}

\newcommand{\comm}[1]{{\color{cyan}{#1}}}

\newcommand{\Sph}{{$S_{\textrm{ph}}$}}
\newcommand{\RHK}{{$R'_{\textrm{HK}}$}}

\newcommand{\unsw}{University of New South Wales}
\newcommand{\chicago}{Department of Astronomy and Astrophysics, University of
Chicago, 5640 S. Ellis Ave, Chicago, IL 60637, USA}

\newcommand{\grfp}{NSF Graduate Research Fellow}

\newcommand{\flatiron}{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}


%\submitted{for May 2, 2016}

\begin{document}
\title{DS Tuc b is Aligned?}

\shorttitle{DS Tuc R-M} 
\shortauthors{Montet et al.}


\author[0000-0001-7516-8308]{Benjamin~T.~Montet}
\affiliation{\unsw}
\affiliation{\chicago}

\author[0000-0002-9464-8101]{Adina~D.~Feinstein}
\altaffiliation{\grfp}
\affiliation{\chicago}

\author{Rodrigo}

\author{Began Medell}

\author{Pablo}

\author{And others TBD incl. PFS Team}

\author{Erin Flowers}


\correspondingauthor{Benjamin~T.~Montet; \twitter{benmontet}}
\email{bmontet@uchicago.edu}

%@arxiver{f8a.pdf,f5.pdf,f2b.pdf}
%\date{\today, \currenttime}

\begin{abstract}

We'll put an abstract here. comment from Luke: is this the youngest planet with an R-M? it might be?
\end{abstract}

\keywords{This is where we'll put keywords}


 
\section{Introduction} \label{sec:intro}

Planet formation is poorly understood \citep[e.g.][]{Morbidelli16}. 
Each discovered planetary system represents an outcome of the planet formation process, and therefore provides an opportunity to learn about how different planets form in different environments. 
However, each observed present-day system is not a pure laboratory: over billions of years, planet-planet and planet-star gravitational interactions can scatter, torque, migrate, or otherwise perturb orbits, distancing planetary systems from their formation state \citep{Kozai62, Lidov62, Fabrycky07, Chatterjee08}. 
This picture is complicated by the fact that in many cases, stellar ages are very poorly known \citep[e.g.][]{Barnes07, Soderblom10}.

The origins of hot Jupiters are still unclear \citep{Dawson18}.
Kozai-Lidov cycles and tidal friction are often invoked to explain the formation of hot Jupiters \citep{Fabrycky07}, but smooth disk migration provides a reasonable alternative in many cases \citep{Ida08}. 
It is possible that multiple channels are required in order to explain all of the observed systems: \citet{Nelson17} analyze data from the HAT and WASP exoplanet surveys and find the data can be well-fit by a model in which $\sim85\%$ of hot Jupiters are formed through high-eccentricity migration and $\sim15\%$ through disk migration.

Planets in young clusters are valuable resources to provide clean test cases for planet formation. 
Dynamical interactions like the Kozai-Lidov effect can, depending on the system architecture, occur over hundreds of millions or billions of years \citep{Montet15c, Naoz16}. 
For systems with younger ages, we can rule out certain dynamical interactions, meaning it is likely that the orbit of the planet traces the orbit of the now-dissipated disk. 

Therefore, by measuring the obliquity of the orbits of young planets relative to the spin of their host stars, we are tracing the obliquity of their disks. 
Observing a population of these systems will allow us to understand statistical disk properties. 
Alignment of planetary systems and their host stars is often taken as evidence in favor of smooth migration processes. \btmtodo{cite papers here}. 
However, \btmtodo{Batygin citation} suggest wide binary companions or nearby stars in the birth cluster can torque disks to random inclinations over the lifetime of the disk. With a statistical sample of the obliquities of young planets, we can test this hypothesis.

Such a survey is limited by the small number of planetary systems around young stars. There are only a handful of planets known to be younger than 100 Myr, identified by their membership in young moving groups or star forming regions \btmtodo{citep David19, Mann, others}.

Recently, data from the Transiting Exoplanet Survey Satellite \citep{Ricker14} were used to identify a planet around the star DS Tuc A \citep{Bennatti19, Newton19}. 
DS Tuc is a member of the Tucana-Horologium (Tuc-Hor) assocation

DS Tuc is a young star, 45 Myr old. It has a binary but too young for Kozai

The planet traces the disk! 

So is it aligned? Let's learn something.

The rest of this paper is organized as follows:

\section{Observations}

PFS folks will probably have words here.

Mention the fast rotation of the star, vsini of like 17 km/s? And the measured rotation period here. Wouldn't hurt to include the eleanor light curve so people can see the rotation and the magnitude of the spots, and it gets us an easy citation.



\section{Data analysis}

We model the inferred radial velocities with version 1.0.0.dev3 of the \textit{starry} package of \citet{Luger19}. 

\subsection{Likelihood Function}



Something in the models subsubsection about Halpha being less noisy than Shk for this star. Probably because of the wavelengths we're dealing with?

Gee, MCMC sure is cool.


\section{Results}

It's aligned?

\section{Discussion}

\subsection{Long-term trend}

Can we call something that happens over six hours a long-term trend? Let's find out!

Curve goes up in time. Is this another planet?

Feels unlikely based on the magnitude.
Would have to be stellar and not this object and the RVs are stable at the few hundred m/s level from other surveys.

Okay so what's going on?

My theory:
\begin{enumerate}
    \item More spots on the redder side of the star 
    \item Explains additional scatter in second half of transit, noticiable in RV data
    \item Spots are rotating off to high longitude, being increasingly foreshortened.
    \item The means they're blocking less of the red light from the star
    \item makes the star overall redder in time
    \item increases the RV of the star during the transit
\end{enumerate}

We need an OOM estimate that this can increase the RV by 40 m/s in six hours.
Also would affect the shape of the lines but we don't have the raw spectra and I'm not suuuuuper excited about trying to dig in. Maybe one of the PFS folks would want to help with that? 
Maybe Gully would want to help with the general spot math here?

\subsection{Asas-sn data to characterize spots}

\subsection{RM as a powerful technique for young stars}

RVs are hard because the star is so active, but if you can get all the data in one night, it doesn't change that much---or at least in calibratable ways!


But cite Barragan, Aigrain here as the power of RVs in mitigating stellar activity.

\subsubsection{What about oblateness and differential rotation?}

Oblateness - how oblate is the star anyway?
Not important for these systems, just infer a different orbital velocity or radius, depending on how its fit. The only place to learn a difference is in ingress/egress, which needs to be resolved at a high timescale. Need a precise stellar radius and eccentricity, at which point it might be useful! But this is hard for these systems because orbits are hard for these young systems.

cite \citet{Giminez06} in this section probably.


Differential rotation not measureable unless system highly misaligned. Even then the signal is smaller than the scatter due to starspots (1 m/s for a system like this one) so many observations at high SNR will be required to disentangle. This is going to be tough!

Could we say something about differential rotation from multiple planets? This seems at odds with the previous graph. Maybe in idealized cases? Need to work through this consideration!


Somewhere: \citet{Oshagh18} on limitations of R-M for very active stars.

\acknowledgements

We thank \btmtodo{people including Michael Gully-Santiago and Leslie Rogers} for \btmtodo{things}.


This research was enabled by the Exostar19 program at the Kavli Institute for Theoretical Physics at UC Santa Barbara, which was supported in part by the National Science Foundation under Grant No. NSF PHY-1748958.

This project was developed in part at the \textit{Building Early Science with} TESS meeting, which took place in 2019 March at the University of Chicago.

Work by B.T.M. was performed in part under contract with the Jet
Propulsion Laboratory (JPL) funded by NASA through
the Sagan Fellowship Program executed by the NASA
Exoplanet Science Institute.

This material is based upon work supported by the National Science Foundation Graduate Research Fellowship Program under Grant No. (DGE-1746045). Any opinions, findings, and conclusions or recommendations expressed in this material are those of the author(s) and do not necessarily reflect the views of the National Science Foundation.



This paper includes data collected by the TESS mission. Funding for the TESS mission is provided by the NASA Explorer Program.

TESS data were obtained from the Mikulski Archive for Space Telescopes
(MAST).
STScI is operated by the Association of Universities for Research in
Astronomy, Inc., under NASA contract NAS5-26555.
Support for MAST is provided by the NASA Office of Space Science via grant
NNX13AC07G and by other grants and contracts.



\software{%
    numpy \citep{numpy},
    matplotlib \citep{matplotlib},
    scipy \citep{Jones01}
    astropy \citep{Astropy18},
    eleanor \citep{Feinstein19},
    starry \citep{Luger19},
    emcee \citep{Foreman-Mackey12}
    }

\facility{Magellan:Clay (Planet Finder Spectrograph), TESS}





\bibliography{exopapers}






\end{document}

